---
title: "DARewiring Grapher"
author: "Yon Kwon"
date: "1/13/2024"
output: html_document
---

# Grapher for "Design Amidst (Social Behavior)" model

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(R.matlab)
library(tidyverse) # tibble (dataframe)
library(ggplot2) # Plot
library(tidyr) # gather()
library(scales) # pretty_breaks()
library(viridis)
library(ggpp) # Label text position
library(ggsci)
library(ggh4x) # facet nested
```

## Data Import
```{r data_file, eval=FALSE, include=FALSE}{r clear}
rm(list=ls()) # Cleaning R environment
setwd(dirname(rstudioapi::getSourceEditorContext()$path)) # Set SRC DIR as WD
file <- file.choose()

gc()
data <- readMat(file)
fig_id <- paste0(
  basename(file)
)

# label_mech <- c(
#   'atop('Homophily','(Characteristic)')',
#   'atop('Homophily','(Status)')',
#   'Network~Closure',
#   'Preferential~Attachment'
# )
label_mech <- c(
  '(A) Homophily\non Characteristic',
  '(B) Homophily\non Status',
  '(C) Network\nClosure',
  '(D) Preferential\nAttachment'

  # '(A) Homophily',
  # '(B) Homophily',
  # '(B) Network\nClosure',
  # '(C) Preferential\nAttachment'
)
label_mech <- factor(
  label_mech, 
  levels = label_mech
)


label_scenario <- c(
  '(i) No Social Dynamics (Baseline)',
  '(ii) Social Dynamics',
  '(iii) Counterfactual (Random)'
)
# )
# label_scenario <- c(
#   'Social Dynamics',
#   'Counterfactual (Random)',
#   'No Social Dynamics (Baseline)'
# )
label_scenario <- factor(
  label_scenario, 
  levels = label_scenario
)

fig_dpi <- 600
label_size <- 10
tick_label_size <- 8
```
## Figure 1 Summary statistics of hierarchy (Span S)
```{r fig1}
set_fig1_width = 6
set_fig1_height = 3
set_fig1_ylim = c(-.1, .9)

set_fig1_h <- 1
set_fig1_span <- 1:data$para.g.span
# set_fig1_span <- 1:(data$para.g.span-1)
set_fig1_connectivity <- 1
set_fig1_enforcement <- 1
set_fig1_time <- data$para.time

x_label <- bquote('Breadth ('~beta~')')
x_label <- bquote('Span of Control (S)')

txt_scale <- .9

outcome_label <- c(
  '(A) Average Path Legnth',
  # '(B) Organizational Performance'
  '(B) Org. Learning Effectiveness'
)
outcome_label <- factor(
  outcome_label,
  levels = outcome_label
)

df_fig1 <- data.frame()
df_fig1 <- rbind(
  data.frame(
    outcome_label = outcome_label[1],
    span = data$para.a.span[set_fig1_span],
    outcome = data$r.dist.nr.avg[1, 1, set_fig1_span, set_fig1_connectivity, set_fig1_enforcement, set_fig1_time]
  )
  ,
  data.frame(
    outcome_label = outcome_label[2],
    span = data$para.a.span[set_fig1_span],
    outcome = data$r.perf.nr.avg[1, 1, set_fig1_span, set_fig1_connectivity, set_fig1_enforcement, set_fig1_time]
  )
)

axes <- aes(
  x = span,
  y = outcome
)

fig1 <- ggplot(data = df_fig1, mapping = axes) +
  facet_wrap(. ~ outcome_label, scales = 'free', ncol = 3) +
  geom_line(alpha = .9, size = .5) +
  geom_point(size = 1) +
  # scale_shape_manual(values = c(16, 1, 4)) +
  # scale_linetype_manual(values = c('solid', 'dotted', 'dashed')) +
  scale_x_continuous(expand = c(0, .1)) +
  # scale_y_continuous(expand = c(0, .02)) +
  labs(x = x_label, y = NULL) +
  scale_color_npg() +
  theme_bw() +
  theme(
    text = element_text(
      # family = windowsFonts()$serif,
      size = label_size, color = 'black'
    ),
    axis.title = element_text(size = label_size * txt_scale, color = 'black'),
    axis.text = element_text(size = tick_label_size * txt_scale, color = 'black'),
    axis.text.x = element_text(color = 'black'),
    strip.background = element_blank(),
    strip.placement = 'outside',
    strip.text = element_text(size = label_size * txt_scale, color = 'black'),
    panel.spacing = unit(1, 'lines'),
    legend.title = element_blank(),
    legend.position = 'bottom'
  )

fig1
ggsave(
  paste0(
    fig_id, '_',
    'fig1_',
    'span', paste0(data$para.a.span[set_fig1_span], collapse = ","),
    'c', data$para.a.conn[set_fig1_connectivity],
    'e', data$para.a.enfo[set_fig1_enforcement],
    '.png'
  ),
  plot = fig1,
  units = 'in',
  width = set_fig1_width,
  height = set_fig1_height,
  dpi = fig_dpi
)
```



## Figure 2 Span of control * Scenario (Line) * Dynamics (Panel) -> Outcome 
```{r fig2}
# label_size <- 12
# tick_label_size <- 10

# set_fig2_width = 9
# set_fig2_height = 3.5
set_fig2_width = 6.5
set_fig2_height = 3
set_fig2_ylim = c(.1, .7)

set_fig2_mc <- 1:4
# set_fig2_mc <- c(1,3,4)
# set_fig2_mc <- 1
set_fig2_h <- 1
set_fig2_span <- 1:data$para.g.span
# set_fig2_span <- (1:data$para.g.span-1)
set_fig2_connectivity <- 1
set_fig2_enforcement <- 1
set_fig2_t <- data$para.time
# set_fig2_t <- 25

x_label <- 'Span of Control (S)'

y_label <- 'Organizational Performance'
y_label <- 'Org. Learning Effectiveness'
y_value_sc <- data$r.perf.avg
y_value_nr <- data$r.perf.nr.avg
y_value_rr <- data$r.perf.rr.avg

# y_label <- 'Clustering Coefficient'
# y_value_sc <- data$r.clws.avg
# y_value_nr <- data$r.clws.nr.avg
# y_value_rr <- data$r.clws.rr.avg
# 
# y_label <- 'Average Path Length'
# y_value_sc <- data$r.dist.avg
# y_value_nr <- data$r.dist.nr.avg
# y_value_rr <- data$r.dist.rr.avg

# y_label <- 'Belief Diversity'
# y_value_sc <- data$r.disa.avg
# y_value_nr <- data$r.disa.nr.avg
# y_value_rr <- data$r.disa.rr.avg
# 
# y_label <- 'Closeness Centralization'
# y_value_sc <- data$r.cent.avg
# y_value_nr <- data$r.cent.nr.avg
# y_value_rr <- data$r.cent.rr.avg

# y_label <- 'Redundancy'
# y_value_sc <- data$r.clus.avg
# y_value_nr <- data$r.clus.nr.avg
# y_value_rr <- data$r.clus.rr.avg
# 
# y_label <- 'Communication Efficiency'
# y_value_sc <- data$r.effi.avg
# y_value_nr <- data$r.effi.nr.avg
# y_value_rr <- data$r.effi.rr.avg
# 
# y_label <- 'Average Distance'
# y_value_sc <- data$r.dist.avg
# y_value_nr <- data$r.dist.nr.avg
# y_value_rr <- data$r.dist.rr.avg
# 
# y_label <- 'Cumulative Dynamics'
# y_value_sc <- data$r.rewc.avg
# y_value_nr <- data$r.rewc.avg
# y_value_rr <- data$r.rewc.avg

# y_label <- 'Density'
# y_value_sc <- data$r.dens.avg
# y_value_nr <- data$r.dens.nr.avg
# y_value_rr <- data$r.dens.rr.avg

# y_label <- 'Modularity'
# y_value_sc <- data$r.bcva.avg
# y_value_nr <- data$r.bcva.nr.avg
# y_value_rr <- data$r.bcva.rr.avg

df_fig2 <- data.frame()
panel_index <- 0
for (mc in set_fig2_mc) {
  df_next <- data.frame(
    mechanism = label_mech[mc],
    span = data$para.a.span[set_fig2_span],
    scenario = label_scenario[1],
    outcome = y_value_nr[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t],
    span_opt = data$para.a.span[which.max(y_value_nr[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t])],
    y_opt = y_value_nr[mc, set_fig2_h, which.max(y_value_nr[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]), set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]
  )
  df_fig2 <- rbind(df_fig2, df_next)
  
  df_next <- data.frame(
    mechanism = label_mech[mc],
    span = data$para.a.span[set_fig2_span],
    scenario = label_scenario[2],
    outcome = y_value_sc[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t],
    span_opt = data$para.a.span[which.max(y_value_sc[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t])],
    y_opt = y_value_sc[mc, set_fig2_h, which.max(y_value_sc[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]), set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]
  )
  df_fig2 <- rbind(df_fig2, df_next)
  
  df_next <- data.frame(
    mechanism = label_mech[mc],
    span = data$para.a.span[set_fig2_span],
    scenario = label_scenario[3],
    outcome = y_value_rr[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t],
    span_opt = data$para.a.span[which.max(y_value_rr[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t])],
    y_opt = y_value_rr[mc, set_fig2_h, which.max(y_value_rr[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]), set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]
  )
  df_fig2 <- rbind(df_fig2, df_next)
}

axes <- aes(
  x = span,
  y = outcome,
  color = scenario,
  shape = scenario,
  linetype = scenario
)

# df_fig2[df_fig2$scenario == label_scenario[1],]$outcome = NA
# df_fig2[df_fig2$scenario == label_scenario[1],]$y_opt = NA
# df_fig2[df_fig2$scenario == label_scenario[2],]$outcome = NA
# df_fig2[df_fig2$scenario == label_scenario[2],]$y_opt = NA

fig2 <- ggplot(data = df_fig2, mapping = axes) +
  # facet_grid(.~mechanism, labeller = label_parsed) +
  facet_grid(. ~ mechanism) +
  # geom_text_npc(aes(label = panel_label, npcx='right', npcy='bottom'), size=4, colour='black') +
  geom_line(alpha = .9, size = .5) +
  geom_point(size = 1) +
  geom_point(aes(x = span_opt, y = y_opt), size = 2, shape=8, show_guide = F) +
  # scale_shape_manual(breaks = label_scenario, values = c(16, 1, 4)) +
  scale_shape_manual(breaks = label_scenario, values = c(4, 1, 16)) +
  # scale_shape_manual(values = c(16, 4)) +
  # scale_linetype_manual(breaks = label_scenario, values = c('solid', 'dotted', 'dashed')) +
  scale_linetype_manual(breaks = label_scenario, values = c('dashed', 'solid', 'dotted')) +
  # scale_linetype_manual(values = c('solid', 'dashed')) +
  scale_x_continuous(expand = c(.02, .02)) +
  # scale_y_continuous(limits = set_fig2_ylim, expand = c(0, .02)) +
  scale_y_continuous(expand = c(0, .02)) +
  labs(x = x_label, y = y_label) +
  # scale_color_npg() +
  scale_color_manual( breaks = label_scenario, values = c("#282728", "#C5050C", "#00B050") ) +
  theme_bw() +
  theme(
    text = element_text(
      # family = windowsFonts()$serif,
      size = label_size, color = 'black'
    ),
    axis.title = element_text(size = label_size, color = 'black'),
    axis.text = element_text(size = tick_label_size, color = 'black'),
    axis.text.x = element_text(
      # angle = 90, vjust = 0.5, hjust=1,
      color = 'black'),
    strip.background = element_blank(),
    strip.placement = 'outside',
    strip.text = element_text(color = 'black'),
    panel.spacing = unit(1, 'lines'),
    legend.title = element_blank(),
    legend.position = 'bottom'
  )

fig2
ggsave(
  paste0(
    fig_id, '_',
    'fig2_', y_label,
    'span', paste0(data$para.a.span[set_fig2_span], collapse = ","),
    'c', data$para.a.conn[set_fig2_connectivity],
    'e', data$para.a.enfo[set_fig2_enforcement],
    't', set_fig2_t,
    '.png'
  ),
  plot = fig2,
  units = 'in',
  width = set_fig2_width,
  height = set_fig2_height,
  dpi = fig_dpi
)
```



## Figure 2X Span of control * * Dynamics (Panel) -> Difference in Scenario and Counterfactual
```{r fig2}
label_size <- 12
tick_label_size <- 10

set_fig2_width = 9
set_fig2_height = 3.5
set_fig2_ylim = c(.1, .7)

set_fig2_mc <- 1:4
# set_fig2_mc <- 1
set_fig2_h <- 1
set_fig2_span <- 1:data$para.g.span
# set_fig2_span <- (1:data$para.g.span-1)
set_fig2_connectivity <- 1
set_fig2_enforcement <- 2
set_fig2_t <- data$para.time
# set_fig2_t <- 25
# set_fig2_t <- 5

x_label <- 'Span of Control (S)'
label_ransys <- c('Random Effect', 'Systematic Effect')
label_ransys <- factor(label_ransys, levels = label_ransys)

y_label <- 'Effect of Social Dynamics'
y_value_sc <- data$r.perf.avg
y_value_nr <- data$r.perf.nr.avg
y_value_rr <- data$r.perf.rr.avg
y_value_system <- data$r.perf.avg - data$r.perf.rr.avg
y_value_random <- data$r.perf.rr.avg - data$r.perf.nr.avg

# y_label <- 'Clustering Coefficient'
# y_value_sc <- data$r.clws.avg
# y_value_nr <- data$r.clws.nr.avg
# y_value_rr <- data$r.clws.rr.avg
# 
# y_label <- 'Average Path Length'
# y_value_sc <- data$r.dist.avg
# y_value_nr <- data$r.dist.nr.avg
# y_value_rr <- data$r.dist.rr.avg

# y_label <- 'Belief Diversity'
# y_value_sc <- data$r.disa.avg
# y_value_nr <- data$r.disa.nr.avg
# y_value_rr <- data$r.disa.rr.avg
# 
# y_label <- 'Closeness Centralization'
# y_value_sc <- data$r.cent.avg
# y_value_nr <- data$r.cent.nr.avg
# y_value_rr <- data$r.cent.rr.avg

# y_label <- 'Redundancy'
# y_value_sc <- data$r.clus.avg
# y_value_nr <- data$r.clus.nr.avg
# y_value_rr <- data$r.clus.rr.avg
# 
# y_label <- 'Communication Efficiency'
# y_value_sc <- data$r.effi.avg
# y_value_nr <- data$r.effi.nr.avg
# y_value_rr <- data$r.effi.rr.avg
# 
# y_label <- 'Average Distance'
# y_value_sc <- data$r.dist.avg
# y_value_nr <- data$r.dist.nr.avg
# y_value_rr <- data$r.dist.rr.avg
# 
# y_label <- 'Cumulative Dynamics'
# y_value_sc <- data$r.rewc.avg
# y_value_nr <- data$r.rewc.avg
# y_value_rr <- data$r.rewc.avg

# y_label <- 'Density'
# y_value_sc <- data$r.dens.avg
# y_value_nr <- data$r.dens.nr.avg
# y_value_rr <- data$r.dens.rr.avg

# y_label <- 'Modularity'
# y_value_sc <- data$r.bcva.avg
# y_value_nr <- data$r.bcva.nr.avg
# y_value_rr <- data$r.bcva.rr.avg

df_fig2 <- data.frame()
panel_index <- 0
for (mc in set_fig2_mc) {
  df_next <- data.frame(
    mechanism = label_mech[mc],
    span = data$para.a.span[set_fig2_span],
    scenario = label_ransys[1],
    outcome = y_value_random[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t],
    span_opt = data$para.a.span[which.max(y_value_sc[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t])],
    y_opt = y_value_sc[mc, set_fig2_h, which.max(y_value_sc[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]), set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]
  )
  df_fig2 <- rbind(df_fig2, df_next)
  
  df_next <- data.frame(
    mechanism = label_mech[mc],
    span = data$para.a.span[set_fig2_span],
    scenario = label_ransys[2],
    outcome = y_value_system[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t],
    span_opt = data$para.a.span[which.max(y_value_rr[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t])],
    y_opt = y_value_rr[mc, set_fig2_h, which.max(y_value_rr[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]), set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]
  )
  df_fig2 <- rbind(df_fig2, df_next)

}

axes <- aes(
  x = span,
  y = outcome,
  color = scenario,
  shape = scenario,
  linetype = scenario
)

# df_fig2[df_fig2$scenario == label_scenario[1],]$outcome = NA
# df_fig2[df_fig2$scenario == label_scenario[1],]$y_opt = NA
# df_fig2[df_fig2$scenario == label_scenario[2],]$outcome = NA
# df_fig2[df_fig2$scenario == label_scenario[2],]$y_opt = NA

fig2 <- ggplot(data = df_fig2, mapping = axes) +
  # facet_grid(.~mechanism, labeller = label_parsed) +
  facet_grid(. ~ mechanism) +
  # geom_text_npc(aes(label = panel_label, npcx='right', npcy='bottom'), size=4, colour='black') +
  geom_line(alpha = .9, size = .5) +
  geom_point(size = 2) +
  # geom_point(aes(x = span_opt, y = y_opt), size = 2, shape=8, show_guide = F) +
  scale_shape_manual(breaks = label_ransys, values = c(0, 7)) +
  scale_linetype_manual(breaks = label_ransys, values = c('solid', 'dashed')) +
  scale_x_continuous(expand = c(.02, .02)) +
  # scale_y_continuous(limits = set_fig2_ylim, expand = c(0, .02)) +
  scale_y_continuous(expand = c(0, .02)) +
  labs(x = x_label, y = y_label) +
  # scale_color_npg() +
  # scale_color_manual( values = c("#E64B35FF", "#4DBBD5FF", "#00A087FF") ) +
  # scale_color_manual( values = c("#C5050C", "#00B050", "#282728") ) +
  scale_color_manual( breaks = label_ransys, values = c("#C5050C", "#282728") ) +
  theme_bw() +
  theme(
    text = element_text(
      # family = windowsFonts()$serif,
      size = label_size, color = 'black'
    ),
    axis.title = element_text(size = label_size, color = 'black'),
    axis.text = element_text(size = tick_label_size, color = 'black'),
    axis.text.x = element_text(
      # angle = 90, vjust = 0.5, hjust=1,
      color = 'black'),
    strip.background = element_blank(),
    strip.placement = 'outside',
    strip.text = element_text(color = 'black'),
    panel.spacing = unit(1, 'lines'),
    legend.title = element_blank(),
    legend.position = 'bottom'
  )

fig2
ggsave(
  paste0(
    fig_id, '_',
    'fig2_', y_label,
    'span', paste0(data$para.a.span[set_fig2_span], collapse = ","),
    'c', data$para.a.conn[set_fig2_connectivity],
    'e', data$para.a.enfo[set_fig2_enforcement],
    't', set_fig2_t,
    '.png'
  ),
  plot = fig2,
  units = 'in',
  width = set_fig2_width,
  height = set_fig2_height,
  dpi = fig_dpi
)
```


## Figure 2 Demonstration of Small worldness (Scenario panels) 
```{r fig2}
set_fig2_width = 6.5
set_fig2_height = 2.8
set_fig2_ylim = c(-.1, .9)

set_fig2_h <- 1
set_fig2_span <- 1:data$para.g.span
# set_fig2_span <- (1:data$para.g.span-1)
set_fig2_connectivity <- 1:data$para.g.conn
set_fig2_connectivity <- c(1, 2, 3)
set_fig2_enforcement <- 1
set_fig2_t <- data$para.time
# set_fig2_t <- 5

x_label <- 'Span of Control (S)'

y_label <- 'Organizational Performance'
y_value_sc <- data$r.perf.avg
y_value_nr <- data$r.perf.nr.avg
y_value_rr <- data$r.perf.rr.avg

param1_label <- 'Average Path Length'
param1_value_sc <- data$r.dist.avg
param1_value_nr <- data$r.dist.nr.avg
param1_value_rr <- data$r.dist.rr.avg

# param2_label <- 'Clustering Coefficient'
# param2_value_sc <- data$r.clus.avg
# param2_value_nr <- data$r.clus.nr.avg
# param2_value_rr <- data$r.clus.rr.avg

param2_label <- 'Clustering Coefficient (WS)'
param2_value_sc <- data$r.clws.avg
param2_value_nr <- data$r.clws.nr.avg
param2_value_rr <- data$r.clws.rr.av

conn_label <- paste0('Connectivity ', data$para.a.conn)
conn_label <- c(
  # paste0('(A) Bare Hierarchy (C=', data$para.a.conn[set_fig2_connectivity[1]], ')'),
  # paste0('(B) 1% Added Interaction (C=', data$para.a.conn[set_fig2_connectivity[2]], ')'),
  # paste0('(C) 5% Added Interaction (C=', data$para.a.conn[set_fig2_connectivity[3]], ')')
  paste0('(A) Bare Hierarchy'),
  paste0('(B) 1% Added Interaction'),
  paste0('(C) 5% Added Interaction')
)
conn_label <- factor(conn_label, levels = conn_label)

param_label <- c(
  '(i) Average Path Length',
  '(ii) Clustering Coefficient'
)
param_label <- factor(param_label, levels = param_label)

df_fig2 <- data.frame()
panel_index <- 0
for (co in set_fig2_connectivity) {
  outcome1 <- param1_value_nr[1, set_fig2_h, set_fig2_span, co, set_fig2_enforcement, set_fig2_t]
  outcome2 <- param2_value_nr[1, set_fig2_h, set_fig2_span, co, set_fig2_enforcement, set_fig2_t]

  df_next <- data.frame(
    param = param_label[1],
    span = data$para.a.span[set_fig2_span],
    connectivity = conn_label[co],
    outcome1 = outcome1,
    outcome2 = outcome2
  )
  df_fig2 <- rbind(df_fig2, df_next)
  
  # df_next <- data.frame(
  #   param = param_label[2],
  #   span = data$para.a.span[set_fig2_span],
  #   connectivity = conn_label[co],
  #   outcome = outcome2
  # )
  # df_fig2 <- rbind(df_fig2, df_next)
}

axes <- aes(
  x = span
)

range1 <- range(df_fig2$outcome1)
range2 <- range(df_fig2$outcome2)

df_fig2$outcome2 <- scales::rescale(df_fig2$outcome2, to = range1)

fig2 <- ggplot(data = df_fig2, mapping = axes) +
  facet_grid(. ~ connectivity) +
  geom_line(aes(y = outcome1, color = param_label[1], linetype = param_label[1]), alpha = .9, size = .5) +
  geom_line(aes(y = outcome2, color = param_label[2], linetype = param_label[2]), alpha = .9, size = .5) +
  scale_x_continuous(expand = c(.02, .02)) +
  scale_y_continuous(
    name = param_label[1],
    sec.axis = sec_axis(~scales::rescale(., to = range2), name=param_label[2])
  ) +
  labs(x = x_label) +
  scale_color_futurama() +
  theme_bw() +
  theme(
    text = element_text(
      # family = windowsFonts()$serif,
      size = label_size, color = 'black'
    ),
    axis.title = element_text(size = label_size, color = 'black'),
    axis.text = element_text(size = tick_label_size, color = 'black'),
    axis.text.x = element_text(
      # angle = 90, vjust = 0.5, hjust=1,
      color = 'black'),
    strip.background = element_blank(),
    strip.placement = 'outside',
    strip.text = element_text(color = 'black'),
    panel.spacing = unit(1, 'lines'),
    legend.title = element_blank(),
    legend.position = 'bottom'
  )

fig2
ggsave(
  paste0(
    fig_id, '_',
    'fig2_', y_label,
    'span', data$para.a.span[set_fig2_span],
    'conn', paste0(data$para.a.conn[set_fig2_connectivity], collapse = ","),
    'e', data$para.a.enfo[set_fig2_enforcement],
    't', set_fig2_t,
    '.png'
  ),
  plot = fig2,
  units = 'in',
  width = set_fig2_width,
  height = set_fig2_height,
  dpi = fig_dpi
)
```





## Figure 5 Demonstration of Small worldness (Outcome panels) 
```{r fig5}
set_fig5_width = 6
set_fig5_height = 3
set_fig5_ylim = c(-.1, .9)
txt_scale <- .9

set_fig5_h <- 1
set_fig5_span <- 1:data$para.g.span
# set_fig5_span <- (1:data$para.g.span-1)
set_fig5_connectivity <- 1:data$para.g.conn
set_fig5_connectivity <- c(1, 2, 3)
set_fig5_enforcement <- 1
set_fig5_t <- data$para.time
# set_fig5_t <- 5

x_label <- 'Span of Control (S)'

param1_label <- 'Average Path Length'
param1_value_sc <- data$r.dist.avg
param1_value_nr <- data$r.dist.nr.avg
param1_value_rr <- data$r.dist.rr.avg

# param2_label <- 'Clustering Coefficient'
# param2_value_sc <- data$r.clus.avg
# param2_value_nr <- data$r.clus.nr.avg
# param2_value_rr <- data$r.clus.rr.avg

param2_label <- 'Clustering Coefficient (WS)'
param2_value_sc <- data$r.clws.avg
param2_value_nr <- data$r.clws.nr.avg
param2_value_rr <- data$r.clws.rr.av

conn_label <- paste0('Connectivity ', data$para.a.conn)
conn_label <- c(
  # paste0('(A) Bare Hierarchy (C=', data$para.a.conn[set_fig5_connectivity[1]], ')'),
  # paste0('(B) 1% Added Interaction (C=', data$para.a.conn[set_fig5_connectivity[2]], ')'),
  # paste0('(C) 5% Added Interaction (C=', data$para.a.conn[set_fig5_connectivity[3]], ')')
  paste0('(i) No Social Dynamics (Baseline)'),
  paste0('(ii) 1% Interaction Added'),
  paste0('(iii) 5% Interaction Added')
)
conn_label <- factor(conn_label, levels = conn_label)

param_label <- c(
  '(A) Average Path Length',
  '(B) Clustering Coefficient'
)
param_label <- factor(param_label, levels = param_label)

df_fig5 <- data.frame()
panel_index <- 0
for (co in set_fig5_connectivity) {
  outcome1 <- param1_value_nr[1, set_fig5_h, set_fig5_span, co, set_fig5_enforcement, set_fig5_t]
  outcome2 <- param2_value_nr[1, set_fig5_h, set_fig5_span, co, set_fig5_enforcement, set_fig5_t]

  df_next <- data.frame(
    param = param_label[1],
    span = data$para.a.span[set_fig5_span],
    connectivity = conn_label[co],
    outcome = outcome1
  )
  df_fig5 <- rbind(df_fig5, df_next)
  
  df_next <- data.frame(
    param = param_label[2],
    span = data$para.a.span[set_fig5_span],
    connectivity = conn_label[co],
    outcome = outcome2
  )
  df_fig5 <- rbind(df_fig5, df_next)
}

axes <- aes(
  x = span,
  y = outcome,
  color = connectivity,
  linetype = connectivity
)

range1 <- range(df_fig5$outcome1)
range2 <- range(df_fig5$outcome2)

df_fig5$outcome2 <- scales::rescale(df_fig5$outcome2, to = range1)

fig5 <- ggplot(data = df_fig5, mapping = axes) +
  # facet_grid(. ~ param, scales = 'free_y', independent='y') +
  ggh4x::facet_grid2(. ~ param, scales = "free_y", independent = "y") +
  geom_line(alpha = .9, size = .5) +
  scale_color_manual(breaks = conn_label, values = c("#282728", "#76161a", "#C5050C")) +
  geom_point(aes(shape=connectivity), size = 2) +
  scale_shape_manual(breaks = conn_label, values = c(48,49,53)) +
  labs(x = x_label, y='') +
  scale_x_continuous(expand = c(.02, .02)) +
  theme_bw() +
  theme(
    text = element_text(
      size = label_size, color = 'black'
    ),
    axis.title = element_text(size = label_size*txt_scale, color = 'black'),
    axis.text = element_text(size = tick_label_size*txt_scale, color = 'black'),
    axis.text.x = element_text(
      # angle = 90, vjust = 0.5, hjust=1,
      color = 'black'),
    strip.background = element_blank(),
    strip.placement = 'outside',
    strip.text = element_text(size= label_size*txt_scale, color = 'black'),
    panel.spacing = unit(1, 'lines'),
    legend.title = element_blank(),
    legend.position = 'bottom'
  )

fig5
ggsave(
  paste0(
    fig_id, '_',
    'fig5_',
    'span', data$para.a.span[set_fig5_span],
    'conn', paste0(data$para.a.conn[set_fig5_connectivity], collapse = ","),
    'e', data$para.a.enfo[set_fig5_enforcement],
    't', set_fig5_t,
    '.png'
  ),
  plot = fig5,
  units = 'in',
  width = set_fig5_width,
  height = set_fig5_height,
  dpi = fig_dpi
)
```





## Figure 2 Span of control * Connectivity (Line) * Dynamics (Panel) -> Outcome 
```{r fig2}
set_fig2_width = 6
set_fig2_height = 3
set_fig2_ylim = c(-.1, .9)

set_fig2_h <- 1
set_fig2_span <- 1:data$para.g.span
set_fig2_mc <- 1:4
# set_fig2_span <- (1:data$para.g.span-1)
set_fig2_connectivity <- 1
set_fig2_enforcement <- 1
set_fig2_t <- data$para.time
# set_fig2_t <- 5

x_label <- 'Span of Control (S)'

y_label <- 'Organizational Performance'
y_value_sc <- data$r.perf.avg
y_value_nr <- data$r.perf.nr.avg
y_value_rr <- data$r.perf.rr.avg

param1_label <- 'Average Path Length'
param1_value_sc <- data$r.dist.avg
param1_value_nr <- data$r.dist.nr.avg
param1_value_rr <- data$r.dist.rr.avg

param2_label <- 'Clustering Coefficient'
param2_value_sc <- data$r.clus.avg
param2_value_nr <- data$r.clus.nr.avg
param2_value_rr <- data$r.clus.rr.avg

# param2_label <- 'Clustering Coefficient (WS)'
# param2_value_sc <- data$r.clws.avg
# param2_value_nr <- data$r.clws.nr.avg
# param2_value_rr <- data$r.clws.rr.av

conn_label <- factor(conn_label, levels = conn_label)

param_label <- c(
  '(i) Average Path Length',
  '(ii) Clustering Coefficient'
)
param_label <- factor(param_label, levels = param_label)

df_fig2 <- data.frame()
panel_index <- 0
for (mc in set_fig2_mc) {
  outcome1 <- param1_value_sc[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]
  outcome2 <- param2_value_sc[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]
  df_next <- data.frame(
    mechanism = label_mech[mc],
    param = param_label[1],
    span = data$para.a.span[set_fig2_span],
    outcome1 = outcome1,
    outcome2 = outcome2
  )
  df_fig2 <- rbind(df_fig2, df_next)
}

axes <- aes(
  x = span
)

range1 <- range(df_fig2$outcome1)
range2 <- range(df_fig2$outcome2)

df_fig2$outcome2 <- scales::rescale(df_fig2$outcome2, to = range1)

fig2 <- ggplot(data = df_fig2, mapping = axes) +
  facet_grid(. ~ mechanism) +
  geom_line(aes(y = outcome1, color = param_label[1], linetype = param_label[1]), alpha = .9, size = .5) +
  geom_line(aes(y = outcome2, color = param_label[2], linetype = param_label[2]), alpha = .9, size = .5) +
  scale_x_continuous(expand = c(.02, .02)) +
  scale_y_continuous(
    name = param_label[1],
    sec.axis = sec_axis(~scales::rescale(., to = range2), name=param_label[2])
  ) +
  labs(x = x_label) +
  scale_color_futurama() +
  theme_bw() +
  theme(
    text = element_text(
      # family = windowsFonts()$serif,
      size = label_size, color = 'black'
    ),
    axis.title = element_text(size = label_size, color = 'black'),
    axis.text = element_text(size = tick_label_size, color = 'black'),
    axis.text.x = element_text(
      # angle = 90, vjust = 0.5, hjust=1,
      color = 'black'),
    strip.background = element_blank(),
    strip.placement = 'outside',
    strip.text = element_text(color = 'black'),
    panel.spacing = unit(1, 'lines'),
    legend.title = element_blank(),
    legend.position = 'bottom'
  )

fig2
ggsave(
  paste0(
    fig_id, '_',
    'fig2_', y_label,
    'span', data$para.a.span[set_fig2_span],
    'conn', paste0(data$para.a.conn[set_fig2_connectivity], collapse = ","),
    'e', data$para.a.enfo[set_fig2_enforcement],
    't', set_fig2_t,
    '.png'
  ),
  plot = fig2,
  units = 'in',
  width = set_fig2_width,
  height = set_fig2_height,
  dpi = fig_dpi
)
```


## Figure 2 Span of control * Scenario (Line) * Dynamics (Panel) -> Outcome 
```{r fig2}
set_fig2_width = 6
set_fig2_height = 3
set_fig2_ylim = c(-.1, .9)

set_fig2_h <- 1
set_fig2_span <- 1:data$para.g.span
# set_fig2_span <- (1:data$para.g.span-1)
set_fig2_connectivity <- 1
set_fig2_enforcement <- 1
set_fig2_t <- data$para.time
# set_fig2_t <- 5

x_label <- 'Span of Control (S)'

y_label <- 'Organizational Performance'
y_value_sc <- data$r.perf.avg
y_value_nr <- data$r.perf.nr.avg
y_value_rr <- data$r.perf.rr.avg

# y_label <- 'Belief Diversity'
# y_value_sc <- data$r.disa.avg
# y_value_nr <- data$r.disa.nr.avg
# y_value_rr <- data$r.disa.rr.avg
# 
# y_label <- 'Closeness Centralization'
# y_value_sc <- data$r.cent.avg
# y_value_nr <- data$r.cent.nr.avg
# y_value_rr <- data$r.cent.rr.avg
# 
# y_label <- 'Overall Clustering'
# y_label <- 'Redundancy'
# y_value_sc <- data$r.clus.avg
# y_value_nr <- data$r.clus.nr.avg
# y_value_rr <- data$r.clus.rr.avg
# 
# y_label <- 'Communication Efficiency'
# y_value_sc <- data$r.effi.avg
# y_value_nr <- data$r.effi.nr.avg
# y_value_rr <- data$r.effi.rr.avg
# 
# y_label <- 'Average Distance'
# y_value_sc <- data$r.dist.avg
# y_value_nr <- data$r.dist.nr.avg
# y_value_rr <- data$r.dist.rr.avg
# 
# y_label <- 'Cumulative Dynamics'
# y_value_sc <- data$r.rewc.avg
# y_value_nr <- data$r.rewc.avg
# y_value_rr <- data$r.rewc.avg
# 
y_label <- 'Density'
y_value_sc <- data$r.dens.avg
y_value_nr <- data$r.dens.nr.avg
y_value_rr <- data$r.dens.rr.avg
# # 
# y_label <- 'Modularity'
# y_value_sc <- data$r.bcva.avg
# y_value_nr <- data$r.bcva.nr.avg
# y_value_rr <- data$r.bcva.rr.avg

panel_label <- paste0('Panel ', LETTERS[1:20])
panel_label <- factor(panel_label, levels = panel_label)

df_fig2 <- data.frame()
panel_index <- 0
for (mc in 1:data$para.g.mech) {
  panel_index = panel_index + 1
  df_next <- data.frame(
    panel_label = panel_label[panel_index],
    mechanism = label_mech[mc],
    span = data$para.a.span[set_fig2_span],
    scenario = label_scenario[1],
    outcome = y_value_sc[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]
  )
  
  df_fig2 <- rbind(df_fig2, df_next)
  df_next <- data.frame(
    panel_label = panel_label[panel_index],
    mechanism = label_mech[mc],
    span = data$para.a.span[set_fig2_span],
    scenario = label_scenario[2],
    outcome = y_value_rr[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]
  )
  df_fig2 <- rbind(df_fig2, df_next)
  
  df_next <- data.frame(
    panel_label = panel_label[panel_index],
    mechanism = label_mech[mc],
    span = data$para.a.span[set_fig2_span],
    scenario = label_scenario[3],
    outcome = y_value_nr[mc, set_fig2_h, set_fig2_span, set_fig2_connectivity, set_fig2_enforcement, set_fig2_t]
  )
  df_fig2 <- rbind(df_fig2, df_next)
}

axes <- aes(
  x = span,
  y = outcome,
  color = scenario,
  shape = scenario
)

fig2 <- ggplot(data = df_fig2, mapping = axes) +
  # facet_grid(.~mechanism, labeller = label_parsed) +
  facet_grid(. ~ mechanism) +
  # geom_text_npc(aes(label = panel_label, npcx='right', npcy='bottom'), size=4, colour='black') +
  geom_line(alpha = .9, size = .5) +
  geom_point(size = 1) +
  scale_shape_manual(values = c(16, 1, 4)) +
  scale_linetype_manual(values = c('solid', 'dotted', 'dashed')) +
  scale_x_continuous(expand = c(0, .02)) +
  scale_y_continuous(expand = c(0, .02)) +
  labs(x = x_label, y = y_label) +
  scale_color_npg() +
  theme_bw() +
  theme(
    text = element_text(
      # family = windowsFonts()$serif,
      size = label_size, color = 'black'
    ),
    axis.title = element_text(size = label_size, color = 'black'),
    axis.text = element_text(size = tick_label_size, color = 'black'),
    axis.text.x = element_text(
      # angle = 90, vjust = 0.5, hjust=1,
      color = 'black'),
    strip.background = element_blank(),
    strip.placement = 'outside',
    strip.text = element_text(color = 'black'),
    panel.spacing = unit(1, 'lines'),
    legend.title = element_blank(),
    legend.position = 'bottom'
  )

fig2
ggsave(
  paste0(
    fig_id, '_',
    'fig2_', y_label,
    'span', paste0(data$para.a.span[set_fig2_span], collapse = ","),
    'c', data$para.a.conn[set_fig2_connectivity],
    'e', data$para.a.enfo[set_fig2_enforcement],
    't', set_fig2_t,
    '.png'
  ),
  plot = fig2,
  units = 'in',
  width = set_fig2_width,
  height = set_fig2_height,
  dpi = fig_dpi
)
```


## Figure 3 Optimal Structure
```{r fig2}
set_fig2_width = 6
set_fig2_height = 3
set_fig2_ylim = c(-.1, .9)

set_fig2_h <- 1
set_fig2_span <- data$para.a.span
set_fig2_span <- (as.vector(data$para.n) - set_fig2_span - 1)/set_fig2_span

set_fig2_t <- data$para.time
set_fig2_t <- 200

x_label <-'Rewiring Mechanism'
y_label <- 'Optimal Span of Control'
y_value_sc <- data$r.perf.avg
y_value_nr <- data$r.perf.nr.avg
y_value_rr <- data$r.perf.rr.avg

panel_label <- paste0('Panel ', LETTERS[1:20])
panel_label <- factor(panel_label, levels=panel_label)

df_fig2 <- data.frame()
panel_index <- 0
for( mc in 1:data$para.g.mech ){
  panel_index = panel_index+1
  df_next <- data.frame(
    panel_label = panel_label[panel_index],
    mechanism = label_mech[mc],
    scenario = label_scenario[1],
    outcome = data$para.a.span[which.max(y_value_sc[mc, set_fig2_h, , set_fig2_t])]
  )
  df_fig2 <- rbind(df_fig2, df_next)
  df_next <- data.frame(
    panel_label = panel_label[panel_index],
    mechanism = label_mech[mc],
    scenario = label_scenario[2],
    outcome = data$para.a.span[which.max(y_value_nr[mc, set_fig2_h, , set_fig2_t])]
  )
  df_fig2 <- rbind(df_fig2, df_next)
  df_next <- data.frame(
    panel_label = panel_label[panel_index],
    mechanism = label_mech[mc],
    scenario = label_scenario[3],
    outcome = data$para.a.span[which.max(y_value_rr[mc, set_fig2_h, , set_fig2_t])]
  )
  df_fig2 <- rbind(df_fig2, df_next)
}

axes <- aes(
  fill = scenario,
  x = mechanism,
  y = outcome
)

fig2 <- ggplot(data = df_fig2, mapping = axes) +
  # facet_grid(.~mechanism, labeller = label_parsed) +
  # geom_text_npc(aes(label = panel_label, npcx='right', npcy='bottom'), size=4, colour='black') +
  geom_bar(alpha = .9, position = 'dodge', stat = 'identity', color = NA) +
  scale_y_continuous(expand=c(0,0), ) +
  labs(x = x_label, y = y_label) +
  scale_fill_npg(labels = parse_format()) +
  theme_bw()+
  theme(
    text=element_text(
      # family = windowsFonts()$serif,
      size=label_size, color='black'
    ),
    axis.title=element_text(size=label_size, color='black'),
    axis.text=element_text(size=tick_label_size, color='black'),
    axis.text.x = element_text(color = 'black'),
    strip.background = element_blank(),
    strip.placement = 'outside',
    strip.text = element_text(color = 'black'),
    panel.spacing = unit(1, 'lines'),
    legend.title = element_blank(),
    legend.position = 'bottom'
  )

fig2
ggsave(
  paste0(fig_id, '_',
         'fig2_',
         y_label,
         'span', paste0(data$para.a.span[set_fig2_span], collapse = ","),
         't', set_fig2_t,
         '.png'
         ),
  plot = fig2,
  units = 'in', 
  width = set_fig2_width,
  height = set_fig2_height,
  dpi = fig_dpi
)
```

## Longitudinal Pattern (for Report)
```{r figa}
set_figa_width = 6.5
set_figa_height = 3
set_figa_ylim = c(-.1, .9)

set_figa_h <- 1
set_figa_span <- c(1, data$para.g.span)
set_figa_connectivity <- 1
set_figa_enforcement <- 2
set_figa_t_end <- data$para.time
set_figa_t_end <- 650

set_figa_t <- 1:set_figa_t_end
x_label <- expression(Time~Period~(italic(t)))

y_label <- 'Organizational Performance'
y_value_sc <- data$r.perf.avg
y_value_nr <- data$r.perf.nr.avg
y_value_rr <- data$r.perf.rr.avg

# y_label <- 'Belief Diversity'
# y_value_sc <- data$r.disa.avg
# y_value_nr <- data$r.disa.nr.avg
# y_value_rr <- data$r.disa.rr.avg

# y_label <- 'Closeness Centralization'
# y_value_sc <- data$r.cent.avg
# y_value_nr <- data$r.cent.nr.avg
# y_value_rr <- data$r.cent.rr.avg
#
# y_label <- 'Overall Clustering'
# y_value_sc <- data$r.clus.avg
# y_value_nr <- data$r.clus.nr.avg
# y_value_rr <- data$r.clus.rr.avg

# y_label <- 'Communication Efficiency'
# y_value_sc <- data$r.effi.avg
# y_value_nr <- data$r.effi.nr.avg
# y_value_rr <- data$r.effi.rr.avg

# y_label <- 'Number of Rewiring'
# y_value_sc <- data$r.rewi.avg
# y_value_nr <- data$r.rewi.avg
# y_value_rr <- data$r.rewi.avg

panel_label <- paste0('Panel ', LETTERS[1:20])
panel_label <- factor(panel_label, levels = panel_label)

span_label <- c(
  paste0('S=', data$para.a.span[set_figa_span[1]], ' (Tall)'),
  paste0('S=', data$para.a.span[set_figa_span[2]], ' (Flat)')
)
span_label <- factor(span_label, levels = span_label)

df_figa <- data.frame()
panel_index <- 0
for (mc in 1:data$para.g.mech) {
  for( s in 1:2 ){
    panel_index = panel_index + 1
    df_next <- data.frame(
      panel_label = panel_label[panel_index],
      mechanism = label_mech[mc],
      span = span_label[s],
      scenario = label_scenario[1],
      time = set_figa_t,
      outcome = y_value_sc[mc, set_figa_h, set_figa_span[s], set_figa_connectivity, set_figa_enforcement, set_figa_t]
    )
    df_figa <- rbind(df_figa, df_next)
    
    # df_next <- data.frame(
    #   panel_label = panel_label[panel_index],
    #   mechanism = label_mech[mc],
    #   span = span_label[s],
    #   scenario = label_scenario[2],
    #   time = set_figa_t,
    #   outcome = y_value_rr[mc, set_figa_h, set_figa_span[s], set_figa_connectivity, set_figa_enforcement, set_figa_t]
    # )
    # df_figa <- rbind(df_figa, df_next)

    df_next <- data.frame(
      panel_label = panel_label[panel_index],
      mechanism = label_mech[mc],
      span = span_label[s],
      scenario = label_scenario[3],
      time = set_figa_t,
      outcome = y_value_nr[mc, set_figa_h, set_figa_span[s], set_figa_connectivity, set_figa_enforcement, set_figa_t]
    )
    df_figa <- rbind(df_figa, df_next)
  }
}

axes <- aes(
  x = time,
  y = outcome,
  color = span,
  shape = span,
  linetype = scenario
)

df_figa$time <- df_figa$time-1
df_figa_point <- df_figa[df_figa$time %% 100 == 0,]

figa <- ggplot(data = df_figa, mapping = axes) +
  # facet_grid(.~mechanism, labeller = label_parsed) +
  facet_nested(. ~ mechanism) +
  # geom_text_npc(aes(label = panel_label, npcx='right', npcy='bottom'), size=4, colour='black') +
  geom_line(alpha = .9, size = .5) +
  scale_linetype_manual(values = c('solid', 'dotted', 'dashed')) +
  geom_point(data = df_figa_point, size = 1) +
  scale_shape_manual(values = c(2, 6)) +
  scale_color_aaas() +
  scale_x_continuous(expand = c(0, .02)) +
  scale_y_continuous(expand = c(0, .02)) +
  labs(x = x_label, y = y_label) +
  theme_bw() +
  theme(
    text = element_text(# family = windowsFonts()$serif,
    size = label_size, color = 'black'),
    axis.title = element_text(size = label_size, color = 'black'),
    axis.text = element_text(size = tick_label_size, color = 'black'),
    axis.text.x = element_text(size = tick_label_size*.9, color = 'black'),
    strip.background = element_blank(),
    strip.placement = 'outside',
    strip.text = element_text(color = 'black'),
    panel.spacing = unit(1, 'lines'),
    guide_legend(nrow=2),
    legend.title = element_blank(),
    legend.position = 'bottom'
  )

figa
ggsave(
  paste0(
    fig_id,
    '_',
    'figa_',
    y_label,
    't',
    set_figa_t_end,
    '.png'
  ),
  plot = figa,
  units = 'in',
  width = set_figa_width,
  height = set_figa_height,
  dpi = fig_dpi
)
```






## Longitudinal Pattern
```{r figa}
set_figa_width = 6
set_figa_height = 5
set_figa_ylim = c(-.1, .9)

set_figa_h <- 1
set_figa_span <- 1:data$para.g.span
# set_figa_span <- 1:(data$para.g.span-1)
set_figa_connectivity <- 1:data$para.g.conn
set_figa_enforcement <- 1:data$para.g.enfo
set_figa_t <- 1:data$para.time

x_label <- expression(Span ~ of ~ Control ~ (italic(sigma)))

y_label <- 'Firm Performance'
y_value_sc <- data$r.perf.avg
y_value_nr <- data$r.perf.nr.avg
y_value_rr <- data$r.perf.rr.avg

# y_label <- 'Closeness Centralization'
# y_value_sc <- data$r.cent.avg
# y_value_nr <- data$r.cent.nr.avg
# y_value_rr <- data$r.cent.rr.avg
# #
# y_label <- 'Overall Clustering'
# y_value_sc <- data$r.clus.avg
# y_value_nr <- data$r.clus.nr.avg
# y_value_rr <- data$r.clus.rr.avg
#
# y_label <- 'Network Efficiency'
# y_value_sc <- data$r.effi.avg
# y_value_nr <- data$r.effi.nr.avg
# y_value_rr <- data$r.effi.rr.avg

# y_label <- 'Number of Rewiring'
# y_value_sc <- data$r.rewi.avg
# y_value_nr <- data$r.rewi.avg
# y_value_rr <- data$r.rewi.avg

panel_label <- paste0('Panel ', LETTERS[1:20])
panel_label <- factor(panel_label, levels = panel_label)

connectivity_label <- paste0('C=', data$para.a.conn)
connectivity_label <- factor(connectivity_label, levels = connectivity_label)

enforcement_label <- paste0('E=', data$para.a.enfo)
enforcement_label <- factor(enforcement_label, levels = enforcement_label)

df_figa <- data.frame()
panel_index <- 0
for (mc in 1:data$para.g.mech) {
  for( s in set_figa_span ){
    for (c in set_figa_connectivity) {
      for (e in set_figa_enforcement) {
        panel_index = panel_index + 1
        df_next <- data.frame(
          panel_label = panel_label[panel_index],
          mechanism = label_mech[mc],
          span = data$para.a.span[s],
          scenario = label_scenario[1],
          connectivity = connectivity_label[c],
          enforcement = enforcement_label[e],
          time = set_figa_t,
          outcome = y_value_sc[mc, set_figa_h, s, c, e, set_figa_t]
        )
        df_figa <- rbind(df_figa, df_next)
        
        df_next <- data.frame(
          panel_label = panel_label[panel_index],
          mechanism = label_mech[mc],
          span = data$para.a.span[s],
          scenario = label_scenario[2],
          connectivity = connectivity_label[c],
          enforcement = enforcement_label[e],
          time = set_figa_t,
          outcome = y_value_rr[mc, set_figa_h, s, c, e, set_figa_t]
        )
        df_figa <- rbind(df_figa, df_next)

        df_next <- data.frame(
          panel_label = panel_label[panel_index],
          mechanism = label_mech[mc],
          span = data$para.a.span[s],
          scenario = label_scenario[3],
          connectivity = connectivity_label[c],
          enforcement = enforcement_label[e],
          time = set_figa_t,
          outcome = y_value_nr[mc, set_figa_h, s, c, e, set_figa_t]
        )
        df_figa <- rbind(df_figa, df_next)
      }
    }
  }
}

axes <- aes(
  x = time,
  y = outcome,
  color = span,
  group = span
)

figa <- ggplot(data = df_figa, mapping = axes) +
  # facet_grid(.~mechanism, labeller = label_parsed) +
  facet_nested(scenario ~ mechanism + connectivity) +
  # geom_text_npc(aes(label = panel_label, npcx='right', npcy='bottom'), size=4, colour='black') +
  geom_line(alpha = .9, size = .1) +
  # scale_color_npg() +
  scale_x_continuous(expand = c(0, .02)) +
  scale_y_continuous(expand = c(0, .02)) +
  labs(x = x_label, y = y_label) +
  theme_bw() +
  theme(
    text = element_text(# family = windowsFonts()$serif,
    size = label_size, color = 'black'),
    axis.title = element_text(size = label_size, color = 'black'),
    axis.text = element_text(size = tick_label_size, color = 'black'),
    axis.text.x = element_text(color = 'black'),
    strip.background = element_blank(),
    strip.placement = 'outside',
    strip.text = element_text(color = 'black'),
    panel.spacing = unit(1, 'lines'),
    # legend.title = element_blank(),
    legend.position = 'bottom'
  )

figa
ggsave(
  paste0(
    fig_id,
    '_',
    'figa_',
    y_label,
    'span',
    paste0(data$para.a.span[set_figa_span], collapse = ","),
    't',
    set_figa_t,
    '.png'
  ),
  plot = figa,
  units = 'in',
  width = set_figa_width,
  height = set_figa_height,
  dpi = fig_dpi
)
```